---
title: "Marriage Licenses across different civic centre"
subtitle: "in bar chart"
author: 
  - Hanqing Yang
thanks: "Code and data are available at: LINK."
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(tibble)

data <- read_csv("../data/analysis_data/analysis_data.csv")

```


# Introduction

This paper use data reference from @citeR, @opendatatorotno and @Rohan.
This paper analyzes the number of marriage licenses issued across four civic center regions in Toronto—Etobicoke (ET), North York (NY), Toronto (TO), and Scarborough (SC)—from January 1, 2011, onward.





# Data {#sec-data}

Some of our data is of toronto marriage licenses (@fig-marriages), from @opendatatoronto.


```{r}
#| label: fig-marriages
#| echo: false

data |> 
  ggplot(aes(x = date, y = marriage_licenses, fill =  civic_centre)) +
  geom_bar(stat = "identity", position = "dodge") +
  facet_wrap(~ civic_centre, nrow = 2)  +
  theme_minimal() +
  labs(title = "Marriage Licenses Issued Over Time across 4 region in Toronto",
       x = "Date",
       y = "Number of Marriage Licenses",
       fill = "Civic Centre")

```
The bar plot illustrates the number of marriage licenses issued over time across four different civic center regions in Toronto: Etobicoke (ET), North York (NY), Toronto (TO), and Scarborough (SC). Each panel within the plot represents a different civic center, with bars showing the number of marriage licenses issued on specific dates. The bars are color-coded based on the number of marriage licenses issued, and the plot employs a minimal theme for clarity.







